---
title: "Mini-Project 2"
author: "Shuli Hu, Karina Huang, Iris Dong"
date: "October 31, 2017"
output: html_document
---


## Loading the data

```{r}
library(tidyverse)
library(dplyr)
```

```{r, include=FALSE}
<<<<<<< HEAD
library(tidyverse)
library(dplyr)
=======
>>>>>>> 521d75e56e541d7eb04b56e48f2bfda83bd74260
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```
<<<<<<< HEAD

```{r}
glimpse(house_elections)
```
```{r}
glimpse(contributions)
```
```{r}
glimpse(committees)
```
```{r}
glimpse(candidates)
```

```{r}
## Iris
cand_party <- candidates %>%
  summarise(total = n(),
            R = sum(cand_party_affiliation == "REP"), D = sum(cand_party_affiliation == "DEM")) %>%
  print()
```


=======

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
```

```{r}
## Karina 10.29.17

con <- contributions %>%
  filter(transaction_type == "24E" | transaction_type == "24A") %>%
  mutate(entity_type = ifelse(entity_type == "", "NA", entity_type)) %>%
  group_by(cand_id) %>% 
  summarise(pro.CAN = sum(transaction_amt[entity_type == "CAN" & transaction_type == "24E"]), ## Summarise independent expediture by entity (payee) types and transaction types 
            pro.CCM = sum(transaction_amt[entity_type == "CCM" & transaction_type == "24E"]),
            pro.COM = sum(transaction_amt[entity_type == "COM" & transaction_type == "24E"]),
            pro.IND = sum(transaction_amt[entity_type == "IND" & transaction_type == "24E"]),
            pro.ORG = sum(transaction_amt[entity_type == "ORG" & transaction_type == "24E"]),
            pro.PAC = sum(transaction_amt[entity_type == "PAC" & transaction_type == "24E"]),
            pro.PTY = sum(transaction_amt[entity_type == "PTY" & transaction_type == "24E"]),
            pro.NA = sum(transaction_amt[entity_type == "NA" & transaction_type == "24E"]),
            con.Can = sum(transaction_amt[entity_type == "CAN" & transaction_type == "24A"]),
            con.CCM = sum(transaction_amt[entity_type == "CCM" & transaction_type == "24A"]),
            con.COM = sum(transaction_amt[entity_type == "COM" & transaction_type == "24A"]),
            con.IND = sum(transaction_amt[entity_type == "IND" & transaction_type == "24A"]),
            con.ORG = sum(transaction_amt[entity_type == "ORG" & transaction_type == "24A"]),
            con.PAC = sum(transaction_amt[entity_type == "PAC" & transaction_type == "24A"]),
            con.PTY = sum(transaction_amt[entity_type == "PTY" & transaction_type == "24A"]),
            con.NA = sum(transaction_amt[entity_type == "NA" & transaction_type == "24A"])) %>%
  select(cand_id:con.NA)

cand.id <- c(con$cand_id)

can <- candidates %>% ## New candidate dataset
  filter(cand_id %in% c(cand.id)) %>% ## Filtering out ids not reflected in the contribution dataset
  select(cand_id:cand_office, cand_ici:cand_status) 

election <- full_join(can, con, by = "cand_id") %>% ## New dataset by joining candidate and contribution dataset
   mutate(pro.sum = pro.CAN+pro.CCM+pro.COM+pro.IND+pro.ORG+pro.PAC+pro.PTY+pro.NA, ## Sums of expediture by type
          con.sum = con.Can+con.CCM+con.COM+con.IND+con.ORG+con.PAC+con.PTY+con.NA)

election2 <- election %>%
  gather("type", "amount",pro.CAN:con.NA)
```


con <- contributions %>%  ## New contribution dataset 
  filter(transaction_type == "24E" | transaction_type == "24A") %>% ## Filtering for transaction type: advocating and opposing election
  group_by(cand_id) %>% 
  summarise(pro.CAN = sum(transaction_amt[entity_type == "CAN" & transaction_type == "24E"]), ## Summarise independent expediture by entity (payee) types and transaction types 
            pro.CCM = sum(transaction_amt[entity_type == "CCM" & transaction_type == "24E"]),
            pro.COM = sum(transaction_amt[entity_type == "COM" & transaction_type == "24E"]),
            pro.IND = sum(transaction_amt[entity_type == "IND" & transaction_type == "24E"]),
            pro.ORG = sum(transaction_amt[entity_type == "ORG" & transaction_type == "24E"]),
            pro.PAC = sum(transaction_amt[entity_type == "PAC" & transaction_type == "24E"]),
            pro.PTY = sum(transaction_amt[entity_type == "PTY" & transaction_type == "24E"]),
            con.Can = sum(transaction_amt[entity_type == "CAN" & transaction_type == "24A"]),
            con.CCM = sum(transaction_amt[entity_type == "CCM" & transaction_type == "24A"]),
            con.COM = sum(transaction_amt[entity_type == "COM" & transaction_type == "24A"]),
            con.IND = sum(transaction_amt[entity_type == "IND" & transaction_type == "24A"]),
            con.ORG = sum(transaction_amt[entity_type == "ORG" & transaction_type == "24A"]),
            con.PAC = sum(transaction_amt[entity_type == "PAC" & transaction_type == "24A"]),
            con.PTY = sum(transaction_amt[entity_type == "PTY" & transaction_type == "24A"])) %>%
  select(cand_id:con.PTY)

cand.id <- c(con$cand_id) ## Vector for all ids in the new contribution dataset

can <- candidates %>% ## New candidate dataset
  filter(cand_id %in% c(cand.id)) %>% ## Filtering out ids not reflected in the contribution dataset
  select(cand_id:cand_office, cand_ici:cand_status) 

election <- full_join(can, con, by = "cand_id") %>% ## New dataset by joining candidate and contribution dataset
   mutate(pro.sum = pro.CAN+pro.CCM+pro.COM+pro.IND+pro.ORG+pro.PAC+pro.PTY, ## Sums of expediture by type
          con.sum = con.Can+con.CCM+con.COM+con.IND+con.ORG+con.PAC+con.PTY)

election2 <- election %>%
  gather("type", "amount",pro.CAN:con.PTY)


```{r}
## Karina Test

library(ggplot2)


ggplot(election2, aes(x=cand_office, y=amount, col=type)) + 
  geom_point() + 
  geom_jitter() +
  facet_wrap(~cand_party_affiliation)
```









































>>>>>>> 521d75e56e541d7eb04b56e48f2bfda83bd74260









>>>>>>> 521d75e56e541d7eb04b56e48f2bfda83bd74260
