---
title: "Mini-Project 2"
author: "Shuli Hu, Karina Huang, Iris Dong"
date: "October 31, 2017"
output: html_document
---


## Loading the data

```{r}
library(tidyverse)
library(dplyr)
```

```{r, include=FALSE}

load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```


```{r}
## Karina 10.29.17

con <- contributions %>%
  filter(transaction_type == "24E" | transaction_type == "24A") %>%
  mutate(entity_type = ifelse(entity_type == "", "NA", entity_type)) %>%
  group_by(cand_id) %>% 
  summarise(pro.CAN = sum(transaction_amt[entity_type == "CAN" & transaction_type == "24E"]), ## Summarise independent expediture by entity (payee) types and transaction types 
            pro.CCM = sum(transaction_amt[entity_type == "CCM" & transaction_type == "24E"]),
            pro.COM = sum(transaction_amt[entity_type == "COM" & transaction_type == "24E"]),
            pro.IND = sum(transaction_amt[entity_type == "IND" & transaction_type == "24E"]),
            pro.ORG = sum(transaction_amt[entity_type == "ORG" & transaction_type == "24E"]),
            pro.PAC = sum(transaction_amt[entity_type == "PAC" & transaction_type == "24E"]),
            pro.PTY = sum(transaction_amt[entity_type == "PTY" & transaction_type == "24E"]),
            pro.NA = sum(transaction_amt[entity_type == "NA" & transaction_type == "24E"]),
            con.Can = sum(transaction_amt[entity_type == "CAN" & transaction_type == "24A"]),
            con.CCM = sum(transaction_amt[entity_type == "CCM" & transaction_type == "24A"]),
            con.COM = sum(transaction_amt[entity_type == "COM" & transaction_type == "24A"]),
            con.IND = sum(transaction_amt[entity_type == "IND" & transaction_type == "24A"]),
            con.ORG = sum(transaction_amt[entity_type == "ORG" & transaction_type == "24A"]),
            con.PAC = sum(transaction_amt[entity_type == "PAC" & transaction_type == "24A"]),
            con.PTY = sum(transaction_amt[entity_type == "PTY" & transaction_type == "24A"]),
            con.NA = sum(transaction_amt[entity_type == "NA" & transaction_type == "24A"])) %>%
  select(cand_id:con.NA)
```

```{r}
head(con)
```


```{r}
## Karina
cand.id <- c(con$cand_id)

can <- candidates %>% ## New candidate dataset
  filter(cand_id %in% c(cand.id)) %>% ## Filtering out ids not reflected in the contribution dataset
  select(cand_id:cand_office, cand_ici:cand_status) 

election <- full_join(can, con, by = "cand_id") %>% ## New dataset by joining candidate and contribution dataset
   mutate(pro.sum = pro.CAN+pro.CCM+pro.COM+pro.IND+pro.ORG+pro.PAC+pro.PTY+pro.NA, ## Sums of expediture by type
          con.sum = con.Can+con.CCM+con.COM+con.IND+con.ORG+con.PAC+con.PTY+con.NA)
head(election)
```


```{R}
## Karina
pro <- c("pro.CAN","pro.CCM","pro.COM","pro.IND","pro.ORG","pro.PAC","pro.PTY","pro.NA")
con <- c("con.CAN","con.CCM","con.COM","con.IND","con.IND","con.PAC","con.PTY","con.NA")



election2 <- election %>%
  gather("type", "amount",pro.CAN:con.NA) %>%
  select(cand_id, cand_party_affiliation, type, amount) %>%
  mutate(transaction.type = ifelse(type %in% c(pro), "pro", "con"))

## Iris
election2$entity.type[election2$type %in% c("pro.CAN", "con.CAN")] <- "CAN"
election2$entity.type[election2$type %in% c("pro.CCM", "con.CCM")] <- "CCM"
election2$entity.type[election2$type %in% c("pro.COM", "con.COM")] <- "COM"
election2$entity.type[election2$type %in% c("pro.IND", "con.IND")] <- "IND"
election2$entity.type[election2$type %in% c("pro.ORG", "con.ORG")] <- "ORG"
election2$entity.type[election2$type %in% c("pro.PAC", "con.PAC")] <- "PAC"
election2$entity.type[election2$type %in% c("pro.PTY", "con.PTY")] <- "PTY"
election2$entity.type[election2$type %in% c("pro.NA", "con.NA")] <- "NA"

print(election2)


```


## Iris Test

library(ggplot2)


ggplot(election2, aes(x= entity.type, y = sum(amount), fill=transaction.type)) + 
  geom_bar() + 
  facet_wrap(~cand_party_affiliation)



### Karina 10.29.afternoon
con <- contributions %>%  ## New contribution dataset 
  filter(transaction_type == "24E" | transaction_type == "24A") %>% ## Filtering for transaction type: advocating and opposing election
  group_by(cand_id) %>% 
  summarise(pro.CAN = sum(transaction_amt[entity_type == "CAN" & transaction_type == "24E"]), ## Summarise independent expediture by entity (payee) types and transaction types 
            pro.CCM = sum(transaction_amt[entity_type == "CCM" & transaction_type == "24E"]),
            pro.COM = sum(transaction_amt[entity_type == "COM" & transaction_type == "24E"]),
            pro.IND = sum(transaction_amt[entity_type == "IND" & transaction_type == "24E"]),
            pro.ORG = sum(transaction_amt[entity_type == "ORG" & transaction_type == "24E"]),
            pro.PAC = sum(transaction_amt[entity_type == "PAC" & transaction_type == "24E"]),
            pro.PTY = sum(transaction_amt[entity_type == "PTY" & transaction_type == "24E"]),
            con.Can = sum(transaction_amt[entity_type == "CAN" & transaction_type == "24A"]),
            con.CCM = sum(transaction_amt[entity_type == "CCM" & transaction_type == "24A"]),
            con.COM = sum(transaction_amt[entity_type == "COM" & transaction_type == "24A"]),
            con.IND = sum(transaction_amt[entity_type == "IND" & transaction_type == "24A"]),
            con.ORG = sum(transaction_amt[entity_type == "ORG" & transaction_type == "24A"]),
            con.PAC = sum(transaction_amt[entity_type == "PAC" & transaction_type == "24A"]),
            con.PTY = sum(transaction_amt[entity_type == "PTY" & transaction_type == "24A"])) %>%
  select(cand_id:con.PTY)


cand.id <- c(con$cand_id) ## Vector for all ids in the new contribution dataset


can <- candidates %>% ## New candidate dataset
  filter(cand_id %in% c(cand.id)) %>% ## Filtering out ids not reflected in the contribution dataset
  select(cand_id:cand_office, cand_ici:cand_status) 

election <- full_join(can, con, by = "cand_id") %>% ## New dataset by joining candidate and contribution dataset
   mutate(pro.sum = pro.CAN+pro.CCM+pro.COM+pro.IND+pro.ORG+pro.PAC+pro.PTY, ## Sums of expediture by type
          con.sum = con.Can+con.CCM+con.COM+con.IND+con.ORG+con.PAC+con.PTY)

election2 <- election %>%
  gather("type", "amount",pro.CAN:con.PTY)





































>>>>>>> 521d75e56e541d7eb04b56e48f2bfda83bd74260









>>>>>>> 521d75e56e541d7eb04b56e48f2bfda83bd74260
