---
title: "Mini-Project 2: Federal Election 2012"
author: "Shuli Hu, Karina Huang, Iris Dong"
date: "October 31, 2017"
output: html_document
---

###Issue

a short paragraph introducing what we are looking at


```{r, warning=FALSE, message=FALSE}
#load packages and dataset
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(grid)
library(gridExtra)
```

```{r}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```

```{r, warning=FALSE, message=FALSE}
#Shuli rewrite chunk "Karina 10/29/17 #1 #2"

#create two lists of transaction type and entity type
trans_type_list = c("pro", "con")
entity_type_list = c("CAN", "CCM", "COM", "IND", "ORG", "PAC", "PTY")

#wrangling data in contributions
contributions1 <- contributions %>%
  filter(transaction_type == "24E" | transaction_type == "24A") %>%
  filter(entity_type != "") %>%
  group_by(cand_id) %>%
  summarise(pro.CAN = sum(transaction_amt[entity_type == "CAN" & transaction_type == "24E"]),
            pro.CCM = sum(transaction_amt[entity_type == "CCM" & transaction_type == "24E"]),
            pro.COM = sum(transaction_amt[entity_type == "COM" & transaction_type == "24E"]),
            pro.IND = sum(transaction_amt[entity_type == "IND" & transaction_type == "24E"]),
            pro.ORG = sum(transaction_amt[entity_type == "ORG" & transaction_type == "24E"]),
            pro.PAC = sum(transaction_amt[entity_type == "PAC" & transaction_type == "24E"]),
            pro.PTY = sum(transaction_amt[entity_type == "PTY" & transaction_type == "24E"]),
            con.Can = sum(transaction_amt[entity_type == "CAN" & transaction_type == "24A"]),
            con.CCM = sum(transaction_amt[entity_type == "CCM" & transaction_type == "24A"]),
            con.COM = sum(transaction_amt[entity_type == "COM" & transaction_type == "24A"]),
            con.IND = sum(transaction_amt[entity_type == "IND" & transaction_type == "24A"]),
            con.ORG = sum(transaction_amt[entity_type == "ORG" & transaction_type == "24A"]),
            con.PAC = sum(transaction_amt[entity_type == "PAC" & transaction_type == "24A"]),
            con.PTY = sum(transaction_amt[entity_type == "PTY" & transaction_type == "24A"]))

candidates1 <- candidates %>% ## New candidate dataset
  filter(cand_id %in% c(contributions1$cand_id)) %>% ## get the cand_id exists in both candidates and contributions1 
  select(cand_id:cand_office, cand_ici:cand_status) 

 
#create two lists of pro.type and con.type
pro.type <- c()
con.type <- c()
i=1
while(i<=length(entity_type_list)) {
       a <- paste("pro", entity_type_list[i], sep=".")
       b <- paste("con", entity_type_list[i], sep=".")
       pro.type <- c(pro.type, a)
       con.type <- c(con.type, b)
       i=i+1
 }

#join tables candidates and contributions by candidate ID
election <- full_join(candidates1, contributions1, by = "cand_id") %>% 
  mutate(pro.sum = pro.CAN+pro.CCM+pro.COM+pro.IND+pro.ORG+pro.PAC+pro.PTY, 
          con.sum = con.Can+con.CCM+con.COM+con.IND+con.ORG+con.PAC+con.PTY) %>%
  group_by(cand_party_affiliation) %>%
  summarise(pro.CAN = sum(pro.CAN), pro.CCM = sum(pro.CCM), pro.COM = sum(pro.COM), 
            pro.IND = sum(pro.IND), pro.ORG = sum(pro.ORG), pro.PAC = sum(pro.PAC),
            pro.PTY = sum(pro.PTY), 
            con.CAN = sum(con.Can), con.CCM = sum(con.CCM), con.COM = sum(con.COM),
            con.IND = sum(con.IND), con.ORG = sum(con.ORG), con.PAC = sum(con.PAC),
            con.PTY = sum(con.PTY), pro.sum = sum(pro.sum), con.sum = sum(con.sum)) %>%
  filter(cand_party_affiliation == "DEM" | cand_party_affiliation == "REP") %>%
  gather("type", "amount",pro.CAN:con.PTY) %>%
  mutate(transaction.type = ifelse(type %in% c(pro.type), "pro", "con"),
         entity.type = ifelse(type %in% "pro.CAN" | type %in% "con.CAN", "CAN", 
                              ifelse(type %in% "pro.CCM" | type %in% "con.CCM", "CCM", 
                                     ifelse(type %in% "pro.COM" | type %in% "con.COM", "COM", 
                                            ifelse(type %in% "pro.IND" | type %in% "con.IND", "IND", 
                                                   ifelse(type %in% "pro.ORG" | type %in% "con.ORG", "ORG", 
                                                          ifelse(type %in% "pro.PAC" | type %in% "con.PAC", "PAC",
                                                                 ifelse(type %in% "pro.PTY" | type %in% "con.PTY", "PTY", type)))))))) %>%
  select(-type) %>%
  spread(transaction.type, amount) %>%
  select(-pro.sum, -con.sum) %>%
  gather("transaction.type", "amount", con:pro)
```

###describe the table



```{r, warning=FALSE, message=FALSE}
#Shuli rewrite 10/31/2017 morning

#join tables election
election2 <- election %>%
  group_by(cand_party_affiliation, entity.type) %>%
  summarise(party_entity_total = sum(amount)) #for each party*entity the total amount of transactions

election_total <- left_join(election, election2, by = c("cand_party_affiliation", "entity.type"))

#for only entity type "ORG""
election_org_only <- election2 %>%
  filter(entity.type == "ORG")

election_non_org <- election2 %>%
  filter(!entity.type == "ORG")

print(election_org_only)
party_name <- c(DEM="Democratic",
                REP="Republican")
```


```{r}
print(election2)
summary(election_org_only)
```


###describe the plot

The percentage distribution of contributions

```{r, warning=FALSE, message=FALSE, fig.width=10, fig.height=8, echo=FALSE}
#plot
#percentage distribution of contributions
ggplot(election_total, aes(x = entity.type, y = amount/party_entity_total*100, fill=transaction.type, width = 0.7)) + 
  geom_bar(stat = "identity", alpha=0.8) + 
  facet_grid(cand_party_affiliation~.,labeller=as_labeller(party_name)) +
  labs(title = "Distribution of Contributions \nby Party and Entity Type",x="Entity Type", y="Contributions (%)") +
  theme(plot.title=element_text(size = 18, 
                                face="bold", 
                                family="Helvetica", 
                                hjust=0.5,
                                margin = margin(t=0,r=0,b=20,l=20)), 
        axis.title = element_text(face="bold",size = 15),
        axis.title.x = element_text(margin = margin(t=20,r=0,b=0,l=0)),
        axis.title.y = element_text(margin = margin(t=0,r=20,b=0,l=0)),
        strip.text.y = element_text(face="bold",size = 13),
        strip.background =element_rect(fill="white"),
        legend.title = element_text(face="bold",size=15),
        legend.text = element_text(size=10),
        panel.border=element_blank(), 
        panel.grid=element_blank(),
        panel.margin=unit(2,"lines"))+
  scale_fill_discrete(name="Transaction Type",
                         breaks=c("con", "pro"),
                         labels=c("Opposing election of candidate", "Advocating election of candidate"))
```

###describe the plot

```{r, warning=FALSE, message=FALSE, fig.width=10, fig.height=8, echo=FALSE}
#amount distribution of contributions
p2 <- ggplot(election_non_org, aes(x = entity.type, y = party_entity_total/1000000)) + 
  geom_bar(stat = "identity", 
           alpha = 0.8, fill="blue") + 
  facet_grid(.~cand_party_affiliation,
             labeller=as_labeller(party_name)) +
  labs(title = "Contributions by Party and Entity Type (Non-ORG)",x="Entity Type", y="Amount of Contributions \n(in 'mil USD)", fill="Transaction Type") +
  geom_text(aes(label=round(party_entity_total/1000000, digits=3)), vjust=-0.3, color="black", size=3.5)+
   scale_y_continuous(limits = c(0, 15),
                      breaks = c(0, 5, 12), 
                     labels = c("0", "5", "12"))+
  scale_fill_discrete(name="Transaction Type",
                         breaks=c("con", "pro"),
                         labels=c("Opposing election of candidate", "Advocating election of candidate"))+
  theme(plot.title=element_text(size= 18, 
                                face="bold", 
                                family="Helvetica", 
                                hjust=0.5,
                                margin = margin(t=0,r=0,b=20,l=20)),
        axis.title = element_text(face="bold",size = 15),
        axis.title.x = element_text(margin = margin(t=20,r=0,b=0,l=0)),
        axis.title.y = element_text(margin = margin(t=0,r=20,b=0,l=0)),
        strip.text.x = element_text(face="bold",size = 13),
        strip.background =element_rect(fill="white"),
        legend.title = element_text(face="bold",size=15),
        legend.text = element_text(size=10),
        panel.border=element_blank(), 
        panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank())
  

p3 <- ggplot(election_org_only, aes(x = entity.type, y = party_entity_total/1000000, width=0.15)) + 
  geom_bar(stat = "identity",
           alpha=0.8, 
           fill="blue") + 
  facet_grid(.~cand_party_affiliation,
             labeller=as_labeller(party_name)) +
  labs(title = "Contributions by Party and Entity Type (ORG)",x="Entity Type", y="Amount of Contributions \n(in ‘mil USD)", fill="Transaction Type") +
  geom_text(aes(label=round(party_entity_total/1000000, digits=3)), vjust=-0.3, color="black", size=3.5)+
   scale_y_continuous(limits = c(0,700),
                      breaks = c(0, 300, 600), 
                     labels = c("0", "300", "600"))+
  scale_fill_discrete(name="Transaction Type",
                         breaks=c("con", "pro"),
                         labels=c("Opposing election of candidate", "Advocating election of candidate"))+
  theme(plot.title=element_text(size=18, 
                                face="bold", 
                                family="Helvetica", 
                                hjust=0.5,
                                margin = margin(t=10,r=0,b=20,l=20)),
        axis.title = element_text(face="bold",size = 15),
        axis.title.x = element_text(margin = margin(t=20,r=0,b=0,l=0)),
        axis.title.y = element_text(margin = margin(t=0,r=20,b=0,l=0)),
        strip.text.x = element_text(face="bold",size = 13),
        strip.background =element_rect(fill="white"),
        legend.title = element_text(face="bold",size=15),
        legend.text = element_text(size=10),
        panel.border=element_blank(), 
        panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank())
 

grid.arrange(p2,p3)
```





==========================scratch paper
```{r, warning=FALSE, message=FALSE}
ggplot(election_org_only, aes(x = entity.type, y = party_entity_total, fill=transaction.type)) + 
  geom_bar(stat = "identity",alpha=0.8) + 
  facet_wrap(~cand_party_affiliation) +
  labs(title = "Distribution of Contributions by Party and Entity Type (ORG)",x="ORG", y="Amount of Contributions (in USD)") +
  theme(plot.title=element_text(size=rel(1), 
                                face="bold", 
                                family="Helvetica", 
                                hjust=0.5), 
        panel.border=element_blank(), 
        panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank(), 
        panel.background=element_blank()) 
```

















```{r}
## Karina 10.29.17 #1

con <- contributions %>%
  filter(transaction_type == "24E" | transaction_type == "24A") %>%
  group_by(cand_id) %>% 
  summarise(pro.CAN = sum(transaction_amt[entity_type == "CAN" & transaction_type == "24E"]), ## Summarise independent expediture by entity (payee) types and transaction types 
            pro.CCM = sum(transaction_amt[entity_type == "CCM" & transaction_type == "24E"]),
            pro.COM = sum(transaction_amt[entity_type == "COM" & transaction_type == "24E"]),
            pro.IND = sum(transaction_amt[entity_type == "IND" & transaction_type == "24E"]),
            pro.ORG = sum(transaction_amt[entity_type == "ORG" & transaction_type == "24E"]),
            pro.PAC = sum(transaction_amt[entity_type == "PAC" & transaction_type == "24E"]),
            pro.PTY = sum(transaction_amt[entity_type == "PTY" & transaction_type == "24E"]),
            con.Can = sum(transaction_amt[entity_type == "CAN" & transaction_type == "24A"]),
            con.CCM = sum(transaction_amt[entity_type == "CCM" & transaction_type == "24A"]),
            con.COM = sum(transaction_amt[entity_type == "COM" & transaction_type == "24A"]),
            con.IND = sum(transaction_amt[entity_type == "IND" & transaction_type == "24A"]),
            con.ORG = sum(transaction_amt[entity_type == "ORG" & transaction_type == "24A"]),
            con.PAC = sum(transaction_amt[entity_type == "PAC" & transaction_type == "24A"]),
            con.PTY = sum(transaction_amt[entity_type == "PTY" & transaction_type == "24A"])) %>%
  select(cand_id:con.PTY)

con
```

amount_sum <- function(entity_type_arg, trans_type_arg) {
  contributions %>%
    summarise(te = sum(transaction_amt[entity_type == entity_type_arg & transaction_type == trans_type_arg]))
}




```{r}
## Karina 10/29/17 #2
cand.id <- c(con$cand_id)

can <- candidates %>% ## New candidate dataset
  filter(cand_id %in% c(cand.id)) %>% ## Filtering out ids not reflected in the contribution dataset
  select(cand_id:cand_office, cand_ici:cand_status) 

pro.type <- c("pro.CAN","pro.CCM","pro.COM","pro.IND","pro.ORG","pro.PAC","pro.PTY")
con.type <- c("con.CAN","con.CCM","con.COM","con.IND","con.ORG","con.PAC","con.PTY")

election <- full_join(can, con, by = "cand_id") %>% 
  mutate(pro.sum = pro.CAN+pro.CCM+pro.COM+pro.IND+pro.ORG+pro.PAC+pro.PTY, 
          con.sum = con.Can+con.CCM+con.COM+con.IND+con.ORG+con.PAC+con.PTY) %>%
  group_by(cand_party_affiliation) %>%
  summarise(pro.CAN = sum(pro.CAN), pro.CCM = sum(pro.CCM), pro.COM = sum(pro.COM), 
            pro.IND = sum(pro.IND), pro.ORG = sum(pro.ORG), pro.PAC = sum(pro.PAC),
            pro.PTY = sum(pro.PTY), 
            con.CAN = sum(con.Can), con.CCM = sum(con.CCM), con.COM = sum(con.COM),
            con.IND = sum(con.IND), con.ORG = sum(con.ORG), con.PAC = sum(con.PAC),
            con.PTY = sum(con.PTY), pro.sum = sum(pro.sum), con.sum = sum(con.sum)) %>%
  filter(cand_party_affiliation == "DEM" | cand_party_affiliation == "REP") %>%
  gather("type", "amount",pro.CAN:con.PTY) %>%
  mutate(transaction.type = ifelse(type %in% c(pro.type), "pro", "con"),
         entity.type = ifelse(type %in% "pro.CAN" | type %in% "con.CAN", "CAN", 
                              ifelse(type %in% "pro.CCM" | type %in% "con.CCM", "CCM", 
                                     ifelse(type %in% "pro.COM" | type %in% "con.COM", "COM", 
                                            ifelse(type %in% "pro.IND" | type %in% "con.IND", "IND", 
                                                   ifelse(type %in% "pro.ORG" | type %in% "con.ORG", "ORG", 
                                                          ifelse(type %in% "pro.PAC" | type %in% "con.PAC", "PAC",
                                                                 ifelse(type %in% "pro.PTY" | type %in% "con.PTY", "PTY", type)))))))) %>%
  select(-type) %>%
  spread(transaction.type, amount) %>%
  select(-pro.sum, -con.sum) %>%
  gather("transaction.type", "amount", con:pro) %>%
  print()
```

```{r}
## Iris 10/29/2017
election2 <- election %>%
  group_by(cand_party_affiliation, entity.type) %>%
  summarise(total = sum(amount)) %>%
  print()
```


```{r}
## Iris 10/29/17
election_total <- left_join(election, election2, by = c("cand_party_affiliation", "entity.type"))
print(election_total)
```

```{r}
##Iris 10/30/17
election_org_only <- election_total %>%
  filter(entity.type == "ORG")
print(election_org_only)
```

```{r}
##Iris 10/30/17
election_non_org <- election_total %>%
  filter(!entity.type == "ORG")
print(election_non_org)
```


pro.type <- c("pro.CAN","pro.CCM","pro.COM","pro.IND","pro.ORG","pro.PAC","pro.PTY","pro.NA")
con.type <- c("con.CAN","con.CCM","con.COM","con.IND","con.ORG","con.PAC","con.PTY","con.NA")

election <- full_join(can, con, by = "cand_id") %>% ## New dataset by joining candidate and contribution dataset
   mutate(pro.sum = pro.CAN+pro.CCM+pro.COM+pro.IND+pro.ORG+pro.PAC+pro.PTY+pro.NA, ## Sums of expediture by type
          con.sum = con.Can+con.CCM+con.COM+con.IND+con.ORG+con.PAC+con.PTY+con.NA)
head(election)




## Karina
pro <- c("pro.CAN","pro.CCM","pro.COM","pro.IND","pro.ORG","pro.PAC","pro.PTY","pro.NA")
con <- c("con.CAN","con.CCM","con.COM","con.IND","con.IND","con.PAC","con.PTY","con.NA")
>>>>>>> f3d9f9395c8f7674cb85dedcd22d3f88b92f3015



election2 <- election %>%
  gather("type", "amount",pro.CAN:con.NA) %>%
  select(cand_id, cand_party_affiliation, type, amount) %>%
  mutate(transaction.type = ifelse(type %in% c(pro.type), "pro", "con"),
         entity.type = ifelse(type %in% "pro.CAN" | type %in% "con.CAN", "CAN", 
                              ifelse(type %in% "pro.CCM" | type %in% "con.CCM", "CCM", 
                                     ifelse(type %in% "pro.COM" | type %in% "con.COM", "COM", 
                                            ifelse(type %in% "pro.IND" | type %in% "con.IND", "IND", 
                                                   ifelse(type %in% "pro.ORG" | type %in% "con.ORG", "ORG", 
                                                          ifelse(type %in% "pro.PAC" | type %in% "con.PAC", "PAC",
                                                                 ifelse(type %in% "pro.PTY" | type %in% "con.PTY", "PTY",
                                                                        ifelse(type %in% "pro.NA" | type %in% "con.NA", "NA", type)))))))))

election3 <- election2 %>%
  filter(cand_party_affiliation == "DEM" | cand_party_affiliation == "REP")

  mutate(transaction.type = ifelse(type %in% c(pro), "pro", "con"))

## Iris
election2$entity.type[election2$type %in% c("pro.CAN", "con.CAN")] <- "CAN"
election2$entity.type[election2$type %in% c("pro.CCM", "con.CCM")] <- "CCM"
election2$entity.type[election2$type %in% c("pro.COM", "con.COM")] <- "COM"
election2$entity.type[election2$type %in% c("pro.IND", "con.IND")] <- "IND"
election2$entity.type[election2$type %in% c("pro.ORG", "con.ORG")] <- "ORG"
election2$entity.type[election2$type %in% c("pro.PAC", "con.PAC")] <- "PAC"
election2$entity.type[election2$type %in% c("pro.PTY", "con.PTY")] <- "PTY"
election2$entity.type[election2$type %in% c("pro.NA", "con.NA")] <- "NA"

print(election2)




### Karina 10.29.afternoon
con <- contributions %>%  ## New contribution dataset 
  filter(transaction_type == "24E" | transaction_type == "24A") %>% ## Filtering for transaction type: advocating and opposing election
  group_by(cand_id) %>% 
  summarise(pro.CAN = sum(transaction_amt[entity_type == "CAN" & transaction_type == "24E"]), ## Summarise independent expediture by entity (payee) types and transaction types 
            pro.CCM = sum(transaction_amt[entity_type == "CCM" & transaction_type == "24E"]),
            pro.COM = sum(transaction_amt[entity_type == "COM" & transaction_type == "24E"]),
            pro.IND = sum(transaction_amt[entity_type == "IND" & transaction_type == "24E"]),
            pro.ORG = sum(transaction_amt[entity_type == "ORG" & transaction_type == "24E"]),
            pro.PAC = sum(transaction_amt[entity_type == "PAC" & transaction_type == "24E"]),
            pro.PTY = sum(transaction_amt[entity_type == "PTY" & transaction_type == "24E"]),
            con.Can = sum(transaction_amt[entity_type == "CAN" & transaction_type == "24A"]),
            con.CCM = sum(transaction_amt[entity_type == "CCM" & transaction_type == "24A"]),
            con.COM = sum(transaction_amt[entity_type == "COM" & transaction_type == "24A"]),
            con.IND = sum(transaction_amt[entity_type == "IND" & transaction_type == "24A"]),
            con.ORG = sum(transaction_amt[entity_type == "ORG" & transaction_type == "24A"]),
            con.PAC = sum(transaction_amt[entity_type == "PAC" & transaction_type == "24A"]),
            con.PTY = sum(transaction_amt[entity_type == "PTY" & transaction_type == "24A"])) %>%
  select(cand_id:con.PTY)


cand.id <- c(con$cand_id) ## Vector for all ids in the new contribution dataset


can <- candidates %>% ## New candidate dataset
  filter(cand_id %in% c(cand.id)) %>% ## Filtering out ids not reflected in the contribution dataset
  select(cand_id:cand_office, cand_ici:cand_status) 

election <- full_join(can, con, by = "cand_id") %>% ## New dataset by joining candidate and contribution dataset
   mutate(pro.sum = pro.CAN+pro.CCM+pro.COM+pro.IND+pro.ORG+pro.PAC+pro.PTY, ## Sums of expediture by type
          con.sum = con.Can+con.CCM+con.COM+con.IND+con.ORG+con.PAC+con.PTY)

election2 <- election %>%
  gather("type", "amount",pro.CAN:con.PTY)
  
  
```{r}
## Iris Test 10.30.17
ggplot(election_non_org, aes(x = entity.type, y = total, fill=transaction.type)) + 
  geom_bar(stat = "identity") + 
  facet_wrap(~cand_party_affiliation)

ggplot(election_org_only, aes(x = entity.type, y = total, fill=transaction.type)) + 
  geom_bar(stat = "identity") + 
  facet_wrap(~cand_party_affiliation)
```
  
  
  

```{r}
## Iris Test 10.29.17
ggplot(election_total, aes(x = entity.type, y = amount/total*100, fill=transaction.type)) + 
  geom_bar(stat = "identity") + 
  facet_wrap(~cand_party_affiliation)
```












































