---
title: "Mini-Project 2: Federal Election 2012"
author: "Shuli Hu, Karina Huang, Iris Dong"
date: "October 31, 2017"
output: html_document
---

Different type of entity has different preference of Party. **This report breaks down the entity type of committee and seeks to analyze its preference by looking at their contributions.** Committee entity type includes: 

1. CAN: Candidate 

2. CCM: Candidate Committee

3. COM: Committee

4. IND: Individual (a person)

5. ORG: Organization (not a committee and not a person)

6. PAC: Political Action Committee

7. PTY: Party Organization 

We looked at only the biggest two Parties: Democrats and Republicans. We did not use the interest group category from Committee dataset, because there are too many missing values and the labels are not consistent with entity types[one entity type appears to have been assigned multiple interest group labels].

```{r, warning=FALSE, message=FALSE, echo=FALSE}
#load packages 
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(grid)
library(gridExtra)
```

```{r, echo=FALSE}
#load dataset
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```

```{r, message=FALSE, warning=FALSE}
#Building new contribution dataset
contributions1 <- contributions %>%
  filter(transaction_type == "24E" | transaction_type == "24A") %>% #filtering for transaction types: independent expenditure advocating and opposing individual elections 
  filter(entity_type != "") %>% 
  select(cand_id, transaction_type, transaction_amt, entity_type, cmte_id)

#Building new candidate dataset  
candidates1 <- candidates %>%
  filter(cand_id %in% c(contributions1$cand_id)) %>% #saving only canditate ids that exists in contribution dataset 
  select(cand_id, cand_party_affiliation:cand_office, cand_ici:cand_status) 

#Building new election dataset for use by joining new contribution and candidate dataset
election <- full_join(candidates1, contributions1, by = "cand_id") %>%
  group_by(cand_party_affiliation, entity_type, transaction_type) %>%
  summarise(amount = sum(transaction_amt)) %>% #summarize transaction amount by political parties, entity types and transaction types
  mutate(type = ifelse(transaction_type == "24A", "con", "pro")) %>% #new variable to identify transaction types by pro and con
  filter(cand_party_affiliation == "DEM" | cand_party_affiliation == "REP") %>% #saving only democrats and republicans
  select(-transaction_type) %>%
  na.omit()

election1<- election %>% 
  group_by(cand_party_affiliation, entity_type) %>%
  summarise(total=sum(amount)) #summarize total amount received regardless of transaction type

election <- left_join(election, election1) #adding total amount to election dataset

election_org <- election1 %>%
  filter(entity_type == "ORG") #new dataset for ORG contributions

election_non_org <- election1 %>%
  filter(entity_type != "ORG") #dataset for contributors other than ORG

# vector list for labeling canditate party affiliation
party_name <- c(DEM="Democrats",
                REP="Republicans") 
```

The graph below shows the percentage advocating/opposing distribution of contributions to candidates categorized by different entity type. It shows that Republicans receive more opposing contributions than Democrats. Moreover, some committees obviously prefer one party over the other. For example, Committee, Individual, Political Action Committee prefer Democrats. Party Organizations contribute mainly to advocate instead of opposing. 

```{r, warning=FALSE, message=FALSE, fig.width=13, fig.height=6}
#Plot percentage distribution of contributions. Distinct colors are used for indicating the different transaction types
ggplot(election, aes(x = entity_type, y = amount/total*100, fill=type, width = 0.7)) + 
  geom_bar(stat = "identity", alpha=0.8) + 
  facet_grid(.~cand_party_affiliation,labeller=as_labeller(party_name)) +
  labs(title = "Distribution of Contributions by Party and Entity Type",x="Entity Type", y="Contributions (%)") +
  theme(plot.title=element_text(size = 20, 
                                face="bold", 
                                family="Helvetica", 
                                hjust=0.5,
                                margin = margin(t=0,r=0,b=20,l=20)), 
        axis.title = element_text(face="bold",size = 15),
        axis.title.x = element_text(margin = margin(t=20,r=0,b=0,l=0)),
        axis.title.y = element_text(margin = margin(t=0,r=20,b=0,l=0)),
        strip.text.x = element_text(face="bold",size = 15),
        strip.background =element_rect(fill="white"),
        legend.title = element_text(face="bold",size=15),
        legend.text = element_text(size=10),
        panel.border=element_blank(), 
        panel.grid=element_blank())+
  scale_fill_discrete(name="Transaction Type",
                    breaks=c("con", "pro"),
                    labels=c("Opposing election of candidate", "Advocating election of candidate")) ##Change the legend labels into a more clear desciption

```

The graph below shows the amount of advocating/opposing of contributions classified by entity type. Democrats receive more money in total than Republicans. Organization contributes much more than any other type of committees, so we make a graph for it separately.

```{r, warning=FALSE, message=FALSE, fig.width=13, fig.height=10}
#Amount distribution of contributions.Since the amount of ORG is much larger than the other entity types, we separate the ORG amount for a separate graph as p3, the rest of the entity types are plotted into p2
p2 <- ggplot(election_non_org, aes(x = entity_type, y = total/1000000)) + 
  geom_bar(stat = "identity", 
           alpha = 0.8, fill="#488BC2") + 
  facet_grid(.~cand_party_affiliation,
             labeller=as_labeller(party_name)) +
  labs(title = "Contributions by Party and Entity Type",x="Entity Type (Excluding ORG)", y="Amount of Contributions \n(in 'mil USD)", fill="Transaction Type") +
  geom_text(aes(label=round(total/1000000, digits=3)), vjust=-0.3, color="black", size=3.5)+
   scale_y_continuous(limits = c(0, 15),
                      breaks = c(0, 5, 12), 
                     labels = c("0", "5", "12"))+
  scale_fill_discrete(name="Transaction Type",
                         breaks=c("con", "pro"),
                         labels=c("Opposing election of candidate", "Advocating election of candidate"))+
  theme(plot.title=element_text(size= 18, 
                                face="bold", 
                                family="Helvetica", 
                                hjust=0.5,
                                margin = margin(t=0,r=0,b=20,l=20)),
        axis.title = element_text(face="bold",size = 13),
        strip.text.x = element_text(face="bold",size = 15),
        strip.background =element_rect(fill="white"),
        legend.title = element_text(face="bold",size=15),
        legend.text = element_text(size=10),
        panel.border=element_blank(), 
        panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank())
  

p3 <- ggplot(election_org, aes(x = entity_type, y = total/1000000, width=0.15)) + 
  geom_bar(stat = "identity",
           alpha=0.8, 
           fill="#488BC2") + 
  facet_grid(.~cand_party_affiliation) +
  labs(x="Entity Type", y="Amount of Contributions \n(in ‘mil USD)", fill="Transaction Type") +
  geom_text(aes(label=round(total/1000000, digits=3)), vjust=-0.3, color="black", size=3.5)+
   scale_y_continuous(limits = c(0,700),
                      breaks = c(0, 300, 600), 
                     labels = c("0", "300", "600"))+
  scale_fill_discrete(name="Transaction Type",
                         breaks=c("con", "pro"),
                         labels=c("Opposing election of candidate", "Advocating election of candidate"))+
  theme(plot.title=element_text(size=18, 
                                face="bold", 
                                family="Helvetica", 
                                hjust=0.5,
                                margin = margin(t=10,r=0,b=20,l=20)),
        axis.title = element_text(face="bold",size = 13),
        strip.text.x = element_blank(),
        strip.background =element_rect(fill="white"),
        legend.title = element_text(face="bold",size=15),
        legend.text = element_text(size=10),
        panel.border=element_blank(), 
        panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank())
 
grid.arrange(p2,p3) ##Combine p2 and p3
```
