---
title: "Mini-Project 2"
author: "Shuli Hu, Karina Huang, Iris Dong"
date: "October 31, 2017"
output: html_document
---


## Loading the data

This project is so interesting and relevant to my life!

<<<<<<< HEAD
```{r}
library(tidyverse)
library(dplyr)
```

```{r, include=FALSE}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```



```{r}
#select committees
#Shuli Hu

#select committees
com1 <- committees %>%
  filter(cmte_party_affiliation != "UNK") %>%
  select(cmte_dsgn, org_type, cmte_party_affiliation) 

glimpse(house_elections)
#select house_elction 
house1 <- house_elections %>%
  select(candidate_name, state, party, primary_votes, runoff_votes, general_votes, ge_winner, incumbent)

house1
#try to join tables

```

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
head(house_elections)
```


```{r}
# Karina

Cand.id <- c(candidates$cand_id)

Con <- contributions %>% 
  filter(cand_id %in% Cand.id) %>%
  select(cmte_id,transaction_pgi, entity_type:state, transaction_amt, cand_id, tran_id) 

Can <- candidates %>%
  filter(cand_party_affiliation == "DEM" | cand_party_affiliation == "REP") %>%
  select(cand_id:cand_office_state, cand_ici:cand_pcc) 

Can
```



















































>>>>>>> 521d75e56e541d7eb04b56e48f2bfda83bd74260
